Matching Bullets

### 2015-12-08 imaging-paper.Rnw
adding - yet another bullet-stats csv file.

\begin{figure}
<<tree, echo=FALSE, fig.width=7, fig.height=4, out.width='\\linewidth'>>=
library(rpart)
library(rpart.plot)
CCFs <- read.csv("data-35/bullet-stats.csv")
includes <- setdiff(names(CCFs), c("b1", "b2", "data", "resID", "id.x", "id.y"))
rp1 <- rpart(match~., CCFs[,includes])  # doesn't include cms at all !!!!

@@

CCFs$pred35 <- predict(rp1)
@
\caption{\label{fig:tree}Decision tree of matching bullets based on recursive partitioning.}
\end{figure}

<<pred:table, echo=FALSE, results='asis'>>=
library(xtable)
xtable(xtabs(~I(pred35>0.5)+match, data=CCFs))
@

@@

%' 
%' <<rforest, echo=FALSE>>=
%' library(randomForest)
%' rtrees <- randomForest(factor(match)~., data=CCFs[,includes], ntree=1000)
%' CCFs$forest <- predict(rtrees)
%' importance(rtrees)
%' @
%'

>>>>

\begin{figure}
<<tree, echo=FALSE, fig.width=7, fig.height=4, out.width='\\linewidth'>>=
library(rpart)
library(rpart.plot)
CCFs <- read.csv("data-35-25/bullet-stats.csv")
includes <- setdiff(names(CCFs), c("b1", "b2", "data", "resID", "id.x", "id.y"))
rp1 <- rpart(match~., CCFs[,includes])  # doesn't include cms at all !!!!

@@

CCFs$pred <- predict(rp1)
@
\caption{\label{fig:tree}Decision tree of matching bullets based on recursive partitioning.}
\end{figure}

<<pred:table, echo=FALSE, results='asis'>>=
library(xtable)
xtable(xtabs(~I(pred>0.75)+match, data=CCFs))
@

@@

%' 
%' <<rforest, echo=FALSE>>=
%' library(randomForest)
%' rtrees <- randomForest(factor(match)~., data=CCFs[,includes], ntree=300)
%' qplot(1:nrow(rtrees$err.rate), OOB, geom="line", data=data.frame(rtrees$err.rate)) + theme_bw() + ylim(c(0,NA))
%' CCFs$forest <- predict(rtrees, type="prob")[,2]
%' importance(rtrees)
%' qplot(pred, forest, geom="jitter", data=CCFs, colour=match)
%' @
%'
